R\'esum\'e

### 2019-02-05 resume.tex
Updated resume

%call packages
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.2in]{geometry}
\usepackage{hyperref}

@@

grant.haataja@und.edu

701-580-6305

\url{https://www.linkedin.com/in/grant-haataja-40526a144/}

\url{https://und.joinhandshake.com/users/10782099}

\url{https://github.com/grantHaataja?tab=repositories}

@@

\subsection{University of North Dakota:}
Junior year double major in Computer Science and Mathematics with cumulative GPA of 3.8

\subsection{Williston State College:}
Associate's Degree in Science with High Honors

\subsection{High School:}
Home-schooled, graduated at age 16 with 3.9 GPA

\section{Leadership Experience}

\subsection{Leadership:}
Software Development team co-lead for Advanced Rocketry Club

\subsection{Volunteering:}
Alerus Center - Fight the Frost

@@

\subsubsection{Advanced Engineering and Environmental Services (05/11/17 - 11/18/19)}
\textbf{Engineering Assistant:} Writing daily reports, taking construction photos, GPS data collection and organization, coordinating with contractor and client for smooth project development

@@

\subsection{Technical Skills:}
Java, C, Python, Bash, {\LaTeX}, GitHub, Linux CLI

@@

>>>>

%call packages
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=.9in, top=0.59in]{geometry}
\usepackage{hyperref}

@@

\large grant.haataja@und.edu

\large 701-580-6305

@@

\subsection{University of North Dakota:}
Double major in Computer Science and Mathematics with a current cumulative GPA of 3.80. Expected Graduation Date: 12/2020

\subsection{Williston State College:}
Associate's Degree in Science with High Honors. Graduated in May, 2016 with a cumulative GPA of 3.85

\section{Projects}

\subsection{Advanced Rocketry Club:}
Developing software on embedded computer chips to control the systems of a liquid-propelled rocket for the Base 11 Space Challenge

\subsection{Association of Computing Machinery:}
Participate in regional programming competitions

@@

\subsubsection{Advanced Engineering and Environmental Services (05/11/17 - 11/18/18)}
\textbf{Engineering Assistant:} 
Oversaw and managed 3 construction crews for a 16-mile transmission waterline. Provided quality control on behalf of the client, and coordinated smooth project development

@@

\subsection{Technical Skills:}
Java, C, Python, Bash, GitHub, Linux shell, {\LaTeX}

@@

\section{Links}

\subsection{}
\url{https://www.linkedin.com/in/grant-haataja-40526a144/}

\subsection{}
\url{https://und.joinhandshake.com/users/10782099?buildFromResumeId=9939568}

\subsection{}
\url{https://github.com/grantHaataja?tab=repositories}
